Number recognition for use in a Sudoku solver

### 2012-03-14 doc/icml2010stylefiles/paper.tex
copied latex template
- python nn uses values from config.m
- added some text and overview image to docu

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2010}

@@

@@

\bibliography{example_paper}
\bibliographystyle{icml2010}

>>>>

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Number recognition for use in a Sudoku solver}

@@

\section{Introduction}
Number and letter recognition is key in many real-world applications. Digitalizing print media, automated sorting of letters, or recognition of signs in robotics or driver assistance systems require well performing algorithms for character recognition. In the following we analyze the performance of different techniques for number recognition, namely Neural Networks, Support Vector Machines and Logistic Regression, by using them in an automated sudoku solver.

\section{Overview}
% trim=l b r t
\centerline{\includegraphics[width=\columnwidth, trim=25 10 25 10]{overview}}

blabla

\section{Generation of Training Data}
\subsection{Image Generation}
\subsection{Image Processing}

\section{Training}
\subsection{Neural Network}
\subsection{Support Vector Machine}
\subsection{Logistic Regrssion}

\section{Image Recognition and Preprocessing}

\section{Number Prediction}

\section{Evaluation}

@@

\bibliography{paper}
\bibliographystyle{icml2010}
